Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-04-27 PaperVictor.tex
Agregue rangos angulares en T3

\begin{graphicalabstract}
  \includegraphics[width=\textwidth]{GraphicalAbstract.pdf}
\end{graphicalabstract}

\begin{highlights}
\item We design, optimize, fabricate and characterize
  wideband quasi-omnidirectional (q-OD) structures
  using different approaches.
\item Reflectance averaged over wide spectral range is
  optimized with simple parametrized functions
  (chirped) and by stacking Bragg submirrors.
\item Chirped structure with q-OD bandwidth of 1800 nm
  in the NIR have been demonstrated.
\item Stacking Bragg submirrors resulted in similar
  q-OD band with two third of total physical
  thickness.
\item Agreement between the theoretical and
  experimental results is obtained for porous silicon
  multilayers .
\item Proposed design techniques can be useful for
  obtaining OD dielectric mirrors with different
  materials in large spectral regions.
\end{highlights}

@@

\begin{table}
        \centering
        \begin{tabular}{rrrrr}
                Reference&Year&Sample&ODB (nm)&ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-    &1297-1615&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456 &506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&1321\\
                \hline
                &    &$S_1$&980-1340&360 \\
                This work                               &2021&$S_2$&980-2780&1800\\
                &    &$S_3$&950-2750&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block. We show the attained omnidirectional bands (ODB) and their widths (ODW).}
        \label{tab:table3}
\end{table}

>>>>

%\begin{graphicalabstract}
%  \includegraphics[width=\textwidth]{GraphicalAbstract.pdf}
%\end{graphicalabstract}

%\begin{highlights}
%\item We design, optimize, fabricate and characterize
%  wideband quasi-omnidirectional (q-OD) structures
%  using different approaches.
%\item Reflectance averaged over wide spectral range is
%  optimized with simple parametrized functions
%  (chirped) and by stacking Bragg submirrors.
%\item Chirped structure with q-OD bandwidth of 1800 nm
%  in the NIR have been demonstrated.
%\item Stacking Bragg submirrors resulted in similar
%  q-OD band with two third of total physical
%  thickness.
%\item Agreement between the theoretical and
%  experimental results is obtained for porous silicon
%  multilayers .
%\item Proposed design techniques can be useful for
%  obtaining OD dielectric mirrors with different
%  materials in large spectral regions.
%\end{highlights}

@@

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&ODB (nm)&AR ($^\circ$)&ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
                \hline
                &    &$S_1$&980-1340&10-60&360 \\
                This work                               &2021&$S_2$&980-2780&10-60&1800\\
                &    &$S_3$&950-2750&10-60&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained omnidirectional bands (ODB) in the angular range (AR) and their widths (ODW).}
        \label{tab:table3}
\end{table}
